---
title: "Counting Siblings"
format: html
---

Here are the results of the sibling counting exercise done as part of the [Summer Open And Reproducible Research (SOAR²) Camp](https://ucsb-library-research-data-services.github.io/SOAR2/).

**Goal:** Determine the distribution of the number of siblings among the participants and among the participants' parents.

**Methodology:** Participants randomly sampled and interviewed each other and recorded results on paper sheets, which were then transcribed into individual tabs in a Google spreadsheet, and which were then concatenated.  The raw data therefore contains multiple values per interviewee.

First, let's load the necessary libraries...

```{r message=FALSE}
library(here)
library(googlesheets4)
library(tidyverse)
```

We'll get the data by dynamically reading the camp's Google spreadsheet.  This is highly unusual as a standard practice.  To provide a more realistic example we'll write the data to a local CSV file and then read it back in below as would be more typical.

```{r message=FALSE}
#| code-fold: true
sheets_url <- "https://docs.google.com/spreadsheets/d/1KmVLUnrQ-hVlN5cfTnDcQ4mO_BiKfLhJ7wRp955_Oqw/edit"

# Disable/avoid authentication (assumes the sheet is world-readable)
gs4_deauth()

read_sheet(sheets_url, "Combined") %>%
  select(participant_id, num_siblings, tot_num_parent_siblings) %>%
  write_csv(here("data", "combined_data.csv"))
```

Now read the data from the CSV file and form a single value for each participant by averaging the recorded values.

```{r message=FALSE}
data <- read_csv(here("data", "combined_data.csv")) %>%
  group_by(participant_id) %>%
  summarize(
    avg_siblings = mean(num_siblings),
    avg_parent_siblings = mean(tot_num_parent_siblings)/2
  )
```

The data looks like this:

```{r}
data
```

Now plot a histogram showing the distribution of number of siblings.

```{r}
#| code-fold: true
max_value <- ceiling(max(c(data$avg_siblings, data$avg_parent_siblings)))

data_long <- data %>%
  pivot_longer(
    cols = c(avg_siblings, avg_parent_siblings),
    names_to = "variable",
    values_to = "value"
  )

ggplot(data_long, aes(x=value, fill=variable)) +
  geom_histogram(binwidth=1, position="dodge") +
  ggtitle("Sibling distribution") +
  labs(x="Number of siblings", y="Count", fill="Generation") +
  scale_fill_discrete(
    labels=c(
      "avg_siblings" = "This generation",
      "avg_parent_siblings" = "Previous generation"
    )
  ) +
  scale_x_continuous(breaks=seq(0, max_value))
```

Lastly, let's compare the means of the two distributions.

```{r}

```
